D.I.A.G.R.A.M.: Development of Image Analysis for Graph Recognition And Modeling

### 2025-06-29 doc/article/article.tex
Updated paper

@@

\subsubsection{Relation-Text Association}
After a text box is assigned to a relation, some computation is needed to fully understand how the text is associated to the relation itself. The relation bounding box is then split into three different sections. The overlap between the text bounding box and each of the three sections boxes is computed - then, the section with the highest overlap value is then assigned the text under consideration. \\

\subsubsection{Relationships Building}
Once the text has been dealt with, the last step is to effectively compute which elements are connected by which arrow. This is done by finding, for each arrow, the elements nearer to the head (which we will assume to be the 'target' of the relation) and to the tail (the 'source' of the relationship exemplified by the arrow). These associations are nullified if the distance is above a certain adjustable threshold. This last step is done under the hypothesis that an arrow may come from nothing - or may point to nothing, having actually only either the source or the target.

@@

\subsection{Arrow Orientation}
\label{exp:arrow_orientation}
As we've seen in the previous section, the need to find the exact position of an arrow's head arises (see \textbf{Appendix~\ref{double_clustering}} for a full overview of the first approaches).

@@

>>>>

\subsubsection{Relationships Building}
Once the text has been digitized, it's necessary to effectively compute which elements are connected by which arrows. This is done by finding, for each arrow, the elements nearer to the head (which we will assume to be the 'target' of the relation) and to the tail (the 'source' of the relationship exemplified by the arrow). These associations are nullified if the distance is above a certain adjustable threshold. This last step is done under the hypothesis that an arrow may come from nothing - or may point to nothing, having actually only either the source or the target. \\

@@

\subsubsection{Relation-Text Association}
After a text box is assigned to a relation, some computation is needed to fully understand how the text is associated to the relation itself. The relation's bounding box is then split into three different sections. The overlap between the text bounding box and each of the three sections boxes is computed - then, the section with the highest overlap value is then assigned to the text under consideration.

@@

\subsection{Arrow Orientation}
\label{exp:arrow_orientation}
As we've seen in the previous section, the need to find the exact position of an arrow's head arises (see \textbf{Appendix~\ref{double_clustering} and \textbf{Appendix}~\ref{arrow-net}} for a full overview of the first approaches).

@@

This second approach for determining an arrow's orientation was inspired by UNet \cite{unet}. The core idea was to segment an arrow's bounding box, and to use a specific CNN to try and determine the arrow's head point and the arrow's tail point.

\begin{table}[htbp]
	\centering
	\caption{ArrowNet Architecture Details}
	\label{tab:arrownet}
	\begin{tabular}{|l|l|l|l|l|}
		\hline
		\textbf{Stage} & \textbf{Layer} & \textbf{Input Shape} & \textbf{Output Shape} & \textbf{Operations} \\
		\hline
		\multirow{3}{*}{Encoder} 
		& Encoder1 & $(B, 1, 256, 256)$ & $(B, 32, 256, 256)$ & Double Conv Block \\
		& MaxPool & $(B, 32, 256, 256)$ & $(B, 32, 128, 128)$ & $2 \times 2$ MaxPooling \\
		& Encoder2 & $(B, 32, 128, 128)$ & $(B, 64, 128, 128)$ & Double Conv Block \\
		\hline
		Bottleneck 
		& MaxPool + Bottleneck & $(B, 64, 128, 128)$ & $(B, 128, 64, 64)$ & MaxPool + Double Conv \\
		\hline
		\multirow{4}{*}{Decoder}
		& Upsampling2 & $(B, 128, 64, 64)$ & $(B, 64, 128, 128)$ & Transpose Conv Block \\
		& Skip + Decoder2 & $(B, 128, 128, 128)$ & $(B, 64, 128, 128)$ & Concat + Double Conv \\
		& Upsampling1 & $(B, 64, 128, 128)$ & $(B, 32, 256, 256)$ & Transpose Conv Block \\
		& Skip + Decoder1 & $(B, 64, 256, 256)$ & $(B, 32, 256, 256)$ & Concat + Double Conv \\
		\hline
		Output & Output Conv & $(B, 32, 256, 256)$ & $(B, 3, 256, 256)$ & $1 \times 1$ Convolution \\
		\hline
	\end{tabular}
\end{table}
